Appendix S1: Supporting Information

### 2021-09-02 ms/data_readme.Rmd
Update data readme

```{r manual, include = FALSE, evaluate = FALSE}
# Run these lines if rendering outside of targets plan
library(targets)
library(tarchetypes)
source(here::here("R/packages.R"))
source(here::here("R/functions.R"))
```

@@

# Load objects from targets workflow (all paths to data files)
tar_load(
  c(
    "japan_ferns_comm_full_file",
    "plastome_calibration_dates")
  )
```

@@

Recommended citation for the data: Nitta JH, Mishler BD, Iwasaki W, Ebihara A
(2021) Data from: Spatial phylogenetics of Japanese ferns: Patterns, processes,
and implications for conservation FIXME: add DOI

Citation for and links to publications that cite or use the data: Nitta JH,
Mishler BD, Iwasaki W, Ebihara A (2021) Spatial phylogenetics of Japanese ferns:
Patterns, processes, and implications for conservation <<FIXME: ADD JOURNAL>>

@@

Traits were measured on each species as described in [@Ebihara2019b].

@@

For full methods, see Nitta JH, Mishler BD, Iwasaki W, Ebihara A (2021) Spatial
phylogenetics of Japanese ferns: Patterns, processes, and implications for
conservation <<FIXME: ADD JOURNAL>>

@@

japan_ferns_comm_full.csv: Community matrix (species x sites matrix) of ferns in
Japan. Sites correspond to 0.2 degree x 0.2 degree grid cells covering Japan.
For location of grid cells, see japan_ferns_shape_full.gpkg. Full dataset
including all grid cells (none excluded due to low redundancy).

@@

>>>>

```{r manual, include = FALSE, evaluate = FALSE}
# Run these lines if rendering outside of targets plan
library(targets)
library(tarchetypes)
source(here::here("R/packages.R"))
source(here::here("R/functions.R"))
source(here::here("R/ms_functions.R"))
```

@@

# Load objects from targets workflow (all paths to data files)
tar_load(
  c(
    "ms_functions",
    "japan_ferns_comm_full_file",
    "inext_res_file",
    "occ_point_data_summary_file",
    "plastome_calibration_dates",
    "redundancy_by_res_file",
    "japan_ferns_shape_full_file"
    )
  )
```

@@

Recommended citation for the data: Nitta JH, Mishler BD, Iwasaki W, Ebihara A
(2021) Data from: Spatial phylogenetics of Japanese ferns: Patterns, processes,
and implications for conservation FIXME: add DOI when available

Citation for and links to publications that cite or use the data: Nitta JH,
Mishler BD, Iwasaki W, Ebihara A (2021) Spatial phylogenetics of Japanese ferns:
Patterns, processes, and implications for conservation FIXME: add journal when published

@@

Traits were measured on each species as described in @Ebihara2019b.

@@

For full methods, see Nitta JH, Mishler BD, Iwasaki W, Ebihara A (2021) Spatial
phylogenetics of Japanese ferns: Patterns, processes, and implications for
conservation FIXME: Add journal when published

@@

`r fs::path_file(japan_ferns_comm_full_file)`: Community matrix (species x sites
matrix) of ferns in Japan. Sites correspond to 0.2 degree x 0.2 degree grid
cells covering Japan. For location of grid cells, see
japan_ferns_shape_full.gpkg. Full dataset including all grid cells (none
excluded due to low redundancy).

@@

```{r japan_ferns_inext_results}
inext_res <- read_csv(here::here(inext_res_file))
# Check that no data are missing
assert(inext_res, not_na, everything(), success_fun = success_logical)
```

`r fs::path_file(inext_res_file)`: Output from running iNEXT [@Hsieh2016] on
specimen data for ferns of Japan. iNEXT estimates diversity (here, species
richness) and sampling completeness based on interpolation and extrapolation
from the original data.

Number of variables: `r ncol(inext_res)`

Number of cases/rows: `r nrow(inext_res)`

```{r results = "asis"}
  inext_res %>%
  make_data_desc(
    tribble(
      ~col, ~desc,
      "m", "Sample size (number of individuals)",
      "method", "Method used to estimate diveristy",
      "order", "Diversity order of Hill number (here 0, equivalent to species richness)",
      "qD", "Estimated diversity",
      "qD.LCL", "Lower 95% confidence limit on estimated diversity",
      "qD.UCL", "Upper 95% confidence limit on estimated diversity",
      "SC", "Estimated sampling completeness",
      "SC.LCL", "Lower 95% confidence limit on sampling completeness",
      "SC.UCL", "Upper 95% confidence limit on sampling completeness")
  )
```

```{r occ_point_data_summary}
occ_point_data_summary <- read_csv(here::here(occ_point_data_summary_file))
# Check that no data are missing
assert(occ_point_data_summary, not_na, everything(), success_fun = success_logical)
```

`r fs::path_file(occ_point_data_summary_file)`: Summary of raw specimen data for
native, non-hybrid ferns of Japan. Raw specimen data consists of one row per
specimen, with species name, latitude, longitude, and collection date (raw
specimen data not included here to protect endangered species). Raw data were
filtered to remove duplicate specimens and specimens that occurred outside of
the second-degree mesh (approximately 10 km sq grid cell) map of Japan
(http://www.biodic.go.jp/trialSystem/EN/shpddl.html)

Number of variables: `r ncol(occ_point_data_summary)`

Number of cases/rows: `r nrow(occ_point_data_summary)`

```{r results = "asis"}
  occ_point_data_summary %>%
  make_data_desc(
    tribble(
      ~col, ~desc,
      "dataset", "Dataset name. 'occ_point_data_ferns_unfiltered' indicates data includes all specimens; 'occ_point_data_ferns' indicates data only includes specimens after filtering",
      "variable", "Variable. 'n_taxa' indicates number of taxa, 'n_specimens' indicates number of specimens",
      "value", "Value corresponding to each variable")
  )
```

MD5 checksum: `r tools::md5sum(here::here(occ_point_data_summary_file))`

```{r redundancy_by_res}
redundancy_by_res <- read_csv(here::here(redundancy_by_res_file))
# Check that no data are missing
assert(redundancy_by_res, not_na, everything(), success_fun = success_logical)
```

`r fs::path_file(redundancy_by_res_file)`: Results of testing binning raw
specimen data of native, non-hybrid ferns of Japan into grid-cells at different
resolutions. Sampling redundancy is a metric of sampling completeness,
calculated as 1 - (richness/abundance).

Number of variables: `r ncol(redundancy_by_res)`

Number of cases/rows: `r nrow(redundancy_by_res)`

```{r results = "asis"}
  redundancy_by_res %>%
  make_data_desc(
    tribble(
      ~col, ~desc,
      "res", "Degree of resolution (grid-cell side length), from 0.1 to 0.4 degrees",
      "grids", "Name of grid-cell",
      "abundance", "Number of specimens occurring in grid-cell",
      "richness", "Number of taxa occurring in grid-cell",
      "redundancy", "Redundancy (measure of sampling completeness)"
  ))
```

MD5 checksum: `r tools::md5sum(here::here(redundancy_by_res_file))`

```{r japan_ferns_shape_full}
japan_ferns_shape_full <- st_read(here::here(japan_ferns_shape_full_file))
# Check that no data are missing
assert(japan_ferns_shape_full, not_na, everything(), success_fun = success_logical)
```

`r fs::path_file(japan_ferns_shape_full_file)`: Spatial data of native,
non-hybrid ferns in Japan in GeoPackage format. Compiled from raw specimen data
by binning specimens into 0.2 degree grid cells across Japan.

Number of variables: `r ncol(japan_ferns_shape_full)`

Number of cases/rows: `r nrow(japan_ferns_shape_full)`

```{r results = "asis"}
  japan_ferns_shape_full %>%
  make_data_desc(
    tribble(
      ~col, ~desc,
      "grids", "Name of grid-cell",
      "abundance", "Number of specimens occurring in grid-cell",
      "richness", "Number of taxa occurring in grid-cell",
      "redundancy", "Redundancy (measure of sampling completeness)",
      "geom", "Vector describing shape and position of grid-cell"
  ))
```

MD5 checksum: `r tools::md5sum(here::here(japan_ferns_shape_full_file))`
